---
title: "Shiny Presentation"
author: "Cory Breaux"
date: "3/11/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the App

This app allows the user to plot the locations of earthquakes recorded off the island of Fiji since 1964.

- The userface is simple, comprising a pair of sliders and a Leaflet map to display the output.
- The sliders allow the user to filter the data by the depth of the earthquake or its magnitude.
- At launch, all earthquakes are displayed.
- Zooming in on a specific earthquake and hovering over its marker will display its magnitude and depth.

## About the data

The app uses the default R dataset 'quakes'. The data includes 1000 observations.

```{r quakes, echo = TRUE}
summary(quakes)
```

## A little more about the data

Though this app allows the user to filter the data on depth and magnitude, a quick look at the dataset shows little or no correlation between the two variables. Depth is measured in kilometers, and magnitude is measured according to the Richter Scale.

```{r, echo=TRUE}
plot(x=quakes$depth, y=quakes$mag)
```

## Application Resources

- App link: https://c-breaux.shinyapps.io/FijiQuakes/
- Source code repository: https://github.com/c-breaux/FijiApp